### 2015-11-24 mirror-descent.tex
small typo

\begin{theorem}[First Counter-Example]
\label{theorem:first-counter-example}
Suppose $K = V$. For any $T \ge 42$ there exists a sequence of loss vectors
$\ell_1, \ell_2, \dots, \ell_T \in V^*$ such that $\|\ell_1\|_2 = \|\ell_2\|_2
= \dots = \|\ell_T\|_2 = 1$ and \textsc{Scale-Free Mirror Descent} with
regularizer $R(w) = \frac{1}{2}\|w\|_w^2$, Zinkevich's \textsc{GIGA} algorithm,
and both versions of \textsc{AdaGrad with Composite Mirror Descent Update}
satisfy
$$
\Regret_T(0) \ge \frac{T^{3/2}}{20} \; .
$$
\end{theorem}

>>>>

\begin{theorem}[First Counter-Example]
\label{theorem:first-counter-example}
Suppose $K = V$. For any $T \ge 42$ there exists a sequence of loss vectors
$\ell_1, \ell_2, \dots, \ell_T \in V^*$ such that $\|\ell_1\|_2 = \|\ell_2\|_2
= \dots = \|\ell_T\|_2 = 1$ and \textsc{Scale-Free Mirror Descent} with
regularizer $R(w) = \frac{1}{2}\|w\|_2^2$, Zinkevich's \textsc{GIGA} algorithm,
and both versions of \textsc{AdaGrad with Composite Mirror Descent Update}
satisfy
$$
\Regret_T(0) \ge \frac{T^{3/2}}{20} \; .
$$
\end{theorem}
